---
title: perform featureCounts for caespitosa and tilingii

---

# Load the required library and suppress messages
```{r}
suppressMessages(library(Rsubread))

# Set the working directory
setwd('/scratch/gds44474/MIMULUS/RNAseq_endosperm_til/data/star_pass2')
```

# Define BAM file names for the caespitosa feature counts dataset
```{r}
bam_names_caes <- c(
  'TWN36xUTC1_1_STAR_LVR_v1_MD_Split_Q60.bam',
  'UTC1xTWN36_1_STAR_LVR_v1_MD_Split_Q60.bam',
  'TWN36xUTC1_2_STAR_LVR_v1_MD_Split_Q60.bam',
  'UTC1xTWN36_2_STAR_LVR_v1_MD_Split_Q60.bam',
  'TWN36xUTC1_3_STAR_LVR_v1_MD_Split_Q60.bam',
  'UTC1xTWN36_3_STAR_LVR_v1_MD_Split_Q60.bam'
)
```

# Perform featureCounts for the caespitosa dataset
# I generated MtilingiivarLVRv1.1.primaryTrs.gtf using 05_feature_counts.smk
```{r}
feature_counts_caes <- featureCounts(
  files = bam_names_caes,
  annot.ext = 'MtilingiivarLVRv1.1.primaryTrs.gtf',
  isGTFAnnotationFile = TRUE,
  useMetaFeatures = TRUE,
  countMultiMappingReads = FALSE,
  ignoreDup = FALSE,
  strandSpecific = 2,
  isPairedEnd = TRUE,
  requireBothEndsMapped = TRUE,
  countChimericFragments = FALSE,
  autosort = TRUE,
  nthreads = 6,
  verbose = TRUE
)

# Save the caespitosa dataset result as an RDS file
saveRDS(feature_counts_caes, 'endosperm_counts_caes_object')
```


# Define BAM file names for the tilingii dataset
```{r}
bam_names_til <- c(
  'LVR1xSOP12_1_STAR_LVR_v1_MD_Split_Q60.bam',
  'SOP12xLVR1_1_STAR_LVR_v1_MD_Split_Q60.bam',
  'LVR1xSOP12_2_STAR_LVR_v1_MD_Split_Q60.bam',
  'SOP12xLVR1_2_STAR_LVR_v1_MD_Split_Q60.bam',
  'LVR1xSOP12_3_STAR_LVR_v1_MD_Split_Q60.bam',
  'SOP12xLVR1_3_STAR_LVR_v1_MD_Split_Q60.bam'
)
```

# Perform featureCounts for tilingii dataset
# I generated MtilingiivarLVRv1.1.primaryTrs.gtf using 05_feature_counts.smk
```{r}
feature_counts_til <- featureCounts(
  files = bam_names_til,
  annot.ext = 'MtilingiivarLVRv1.1.primaryTrs.gtf',
  isGTFAnnotationFile = TRUE,
  useMetaFeatures = TRUE,
  countMultiMappingReads = FALSE,
  ignoreDup = FALSE,
  strandSpecific = 2,
  isPairedEnd = TRUE,
  requireBothEndsMapped = TRUE,
  countChimericFragments = FALSE,
  autosort = TRUE,
  nthreads = 6,
  verbose = TRUE
)

# Save the tilingii dataset result as an RDS file
saveRDS(feature_counts_til, 'endosperm_counts_til_object')
```
